\Title

### 2013-02-26 synmut.tex

\begin{figure}
\begin{center}
\subfloat{\includegraphics[height=0.46\linewidth]{reactivities_histograms_syn}
\label{fig:SHAPEA}}
\subfloat{\includegraphics[height=0.46\linewidth]{fixation_probabilities_VnonV}\label{fig:SHAPEB}}
\caption{Permissible synonymous mutations tend to be unpaired.
Panel A) shows the distribution of SHAPE reactivities among sites at which synonymous 
mutations fixed (red), at which mutations reached frequencies above 15\% but
were susequently lost (blue), and sites at which no mutations were observed (green) 
(all categories are restricted to the regions V1-V5$\pm 100$bp).
Sites at which mutations fixed tend to have higher SHAPE reactivities, corresponding to
less base pairing, than those at which mutations are lost.
Sites at which no mutations are observed show an intermediate distribution of SHAPE values.
Panel B) shows the fixation probability of synonymous mutations in
\shankaregion{} separately for variable regions V3-V5 and the connecting conserved 
regions C2-C4 that harbor RNA stems. As expected, the fixation probability is lower
inside the conserved regions. Data from Refs.~\cite{shankarappa_consistent_1999,
bunnik_autologous_2008, liu_selection_2006}.}
\label{fig:SHAPE}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\subfloat{\includegraphics[height=0.47\linewidth]{reactivities_histograms_syn.pdf}\label{fig:SHAPEA}}
\subfloat{\includegraphics[height=0.46\linewidth]{fixation_probabilities_VnonV.pdf}\label{fig:SHAPEB}}
\caption{Permissible synonymous mutations tend to be unpaired.
Panel A) shows the distribution of SHAPE reactivities among sites at which synonymous 
mutations fixed (red), at which mutations reached frequencies above 15\% but
were susequently lost (blue), and sites at which no mutations were observed (green) 
(all categories are restricted to the regions V1-V5$\pm 100$bp).
Sites at which mutations fixed tend to have higher SHAPE reactivities, corresponding to
less base pairing, than those at which mutations are lost.
Sites at which no mutations are observed show an intermediate distribution of SHAPE values.
Panel B) shows the fixation probability of synonymous mutations in
\shankaregion{} separately for variable regions V3-V5 and the connecting conserved 
regions C2-C4 that harbor RNA stems. As expected, the fixation probability is lower
inside the conserved regions. Data from Refs.~\cite{shankarappa_consistent_1999,
bunnik_autologous_2008, liu_selection_2006}.}
\label{fig:SHAPE}
\end{center}
\end{figure}
